---
title: "Alcohol vs Seat choice"
author: "Brandon Reyes"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(ucdavis1,aes(y=alcohol,x=Seat))
```
## Now add in boxplot
```{r}
plot(alcohol~Seat,data=ucdavis1)
```
  
  People in the back are drinking the most.  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=ucdavis1)
summary.aov(model1)
```
The P value is 0.000353 < 0.05 that means you reject the null hypothesis.

```{r}
plot(TukeyHSD(model1))
```
## Conclusions

There is no difference the average alcohol consumption between middle and the front.

There is a difference in the average alcohol consumption between the middle and back rows. 0 is not the interval there is a difference between the average alcohol consumption between the front and the back rows.
